Frequentist Modelling

### 2024-09-19 notebooks/02-frequentist-modelling.qmd
Update renv.lock I guess

# corr_whole
# corr_aph
# corr_control
```

@@

model_parameters(fit_acc_im) |> display()
```

@@

estimate_means(fit_acc_im, by = "aphantasia", transform = "response") |> display()

estimate_contrasts(fit_acc_im, contrast = "aphantasia", transform = "response", p_adjust = "none") |> display()
```

@@

model_parameters(fit_acc_ex) |> display()
```

@@

estimate_means(fit_acc_ex, by = "aphantasia", transform = "response") |> display()

estimate_contrasts(fit_acc_ex, contrast = "aphantasia", transform = "response", p_adjust = "none") |> display()
```

@@

model_parameters(fit_implicit) |> display()
```

@@

model_parameters(fit_explicit) |> display()
```

@@

model_parameters(fit_finer_i) |> display()

Anova(fit_finer_i, type = 3)
```
:::

@@

model_parameters(fit_finer_e) |> display()

Anova(fit_finer_e, type = 3)
```
:::

>>>>

corr_whole
# corr_aph
# corr_control
```

@@

# model_parameters(fit_acc_im) |> display()

Anova(fit_acc_im)
```

@@

estimate_means(fit_acc_im, by = "color", transform = "response") |> display()

estimate_contrasts(fit_acc_im, contrast = "color", transform = "response", p_adjust = "none") |> display()
```

@@

# model_parameters(fit_acc_ex) |> display()

Anova(fit_acc_ex)
```

@@

estimate_means(fit_acc_ex, by = "color", transform = "response") |> display()

estimate_contrasts(fit_acc_ex, contrast = "color", transform = "response", p_adjust = "none") |> display()
```

@@

# model_parameters(fit_implicit) |> display()

Anova(fit_implicit)
```

@@

# model_parameters(fit_explicit) |> display()

Anova(fit_explicit)
```

@@

# model_parameters(fit_finer_i) |> display()

Anova(fit_finer_i)
```
:::

@@

# model_parameters(fit_finer_e) |> display()

Anova(fit_finer_e)
```
:::
